---
title: "Channels_synthesis_growth_dev_consumption"
author: "Carolyn Cummins"
date: "2023-12-08"
output: html_document
---

This Rmd contains mostly exploratory analyses investigating relationships between consumption, growth, and development. However, we do create MS Figures 5 and S3 in this Rmd. See lines 292-386 and 425-607.

Set working directory to source file location first

Load packages
```{r}

library(dplyr)
library(lme4)
library(lmerTest)
library(tidyverse)

```


```{r}

growth_development <- read.csv("growth_development.csv")
consumption <- read.csv("consumption_rate_to.join.csv")
#as of 28 March 2024, we will use the modeled mass corrected consumption rate (corrected for the modeled bug mass during the trial based on global mean IGR and bug beginning mass)
#we will continue to use this as of 10 July 2025

```


Rename columns and prep dataframes to join
```{r}

growth_development <- growth_development %>% 
           dplyr::rename("exp.start.date" = "Beg.Date",
           "exp.end.date" = "End.Date",
           "days.in.expt" = "Days.in.expt",
           "treatment" = "Temp.TRT",
           "channel" = "Channel",
           "chamber" = "Chamber",
           "leaf" = "Leaf.spp.",
           "beg.length.mm" = "Beg.Length.mm",
           "end.Length.mm"="End.Length.mm",
           "bwp.end"="BWP.end.") %>% 
  select(-c(X))


consumption <- consumption %>% 
  dplyr::rename("c.trial" = "trial",
         "c.trial.start.date" = "date.start",
         "c.trial.end.date" = "date.end",
         "c.trial.days" = "days",
         "leaf"="species",
         "c.trial.mean.temp.C" = "mean_temp_C") %>% 
  select(-c(X))

consumption <- consumption %>% mutate(leaf=case_when(leaf=="A" ~ "Acer",
                                                     leaf=="R" ~ "Rhodo"))

growth_development_consumption <- left_join(growth_development, consumption, by=c("treatment", "channel", "chamber", "leaf"))

```


Some bugs had repeated measurements of consumption. This chunk creates a df where consumption is averaged across all measurements for a given bug, if applicable
```{r}

consumption_ave <- consumption %>% group_by(treatment, channel, chamber, leaf) %>%
  dplyr::summarise(mean_bug_consumption=mean(consumption.bug.mg.day.mcorr.modmasscorr))

growth_development_consumption_averaged <- left_join(growth_development, consumption_ave)

```



Questions and hypotheses about concurrent measurements of growth, development, and consumption rates

- We expect that there are tradeoffs between energy allocation to growth vs. development
- As temperatures rise, there is evidence to show that development rate increases faster than growth rate
- Allocation of consumed carbon to growth vs. development -- can we test this? If so, how?

- Plot consumption rates for bugs that developed black wingpads by the end of the experiment vs. those that did not
- Plot growth rates for bugs that developed black wingpads by the end of the experiment vs. those that did not
  - Do this only at the + 3 and +4 treatments where we actually had bugs with bwp?
  - Maybe we would hypothesize that the bugs that developed faster (i.e., had black wingpads by the end of the experiment) would grow slower?
  - Maybe we would further hypothesize that the bugs that developed faster (i.e., had black wingpads by the end of the experiment) tended to consume food faster?
  - But we would also expect that bugs that consumed food faster would grow more
  - For which parameter is the difference greater between bugs that developed BWP vs. those that did not - growth or consumption? Plot with two y-axes? How do we compare the responses directly?

- Make a plot of growth vs. consumption for the whole dataset - points should be shaped for trial # and colored for temperature
treatment
- Plot growth rate and consumption rate across temperatures on the same plot? Compare slopes to compare effects of temperature? Can we do this? If so how?
- summarize at the channel level first?

Test these three questions first:
- Does developing faster = growing faster?
- Does developing faster = consuming more/faster?
- Does consuming faster = growing faster?
- Does the relationship between consumption rate and growth rate differ by leaf species? Hypothesis: bugs eating Rhodo will have a harder time converting consumed C into biomass, so the relationship between consumption and growth will be dampened for Rhodo relative to Acer.

Developing faster = growing faster?
Only look at this for +3 and +4
```{r}

bwp.growth.consumption.3.4 <- growth_development_consumption %>% filter(treatment==3 | treatment==4) %>% 
  group_by(bwp.end) %>%
  dplyr::summarise(
    average_igr=mean(igr),
    sd_igr=sd(igr),
    n_igr=n(),
    se_igr=sd_igr/sqrt(n_igr),
    
    average_igr=mean(igr),
    sd_igr=sd(igr),
    n_igr=n(),
    se_igr=sd_igr/sqrt(n_igr),
    
    average_cons_bug_mg.mg.day=mean(consumption.bug.mg.day.mcorr.modmasscorr, na.rm=T),
    sd_cons_bug_mg.mg.day=sd(consumption.bug.mg.day.mcorr.modmasscorr, na.rm=T),
    n_cons_bug_mg.mg.day=n(), 
    se_cons_bug_mg.mg.day=sd_cons_bug_mg.mg.day/sqrt(n_cons_bug_mg.mg.day),)

```


IGR by black wingpads
```{r}

options(scipen=10000)

plot.igr.bwp <- ggplot()+
  theme_classic()+
  geom_bar(data=bwp.growth.consumption.3.4, aes(x=bwp.end, y=average_igr, color=bwp.end, fill = bwp.end),
           width = 0.4, position = position_dodge(width=0.5), stat="identity")+  
  theme(axis.title.x = element_blank())+
  ylab("Instantaneous growth rate")+
  geom_errorbar(data=bwp.growth.consumption.3.4,
                aes(x=bwp.end, y= average_igr,
                    ymin=average_igr-se_igr, ymax=average_igr+se_igr,
                    group=bwp.end),
                width=.2, position=position_dodge(width=0.5), color= "black")+
  theme(legend.position='none')+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  scale_x_discrete("bwp.end", labels = c("N" = "No black wingpads", "Y" = "Black wingpads"))+
  scale_color_manual(values=c("black","black"), guide="none")+
  scale_fill_manual(values=c("#EC9A29", "#143642"))+
  scale_y_continuous(limits = c(0, 0.008), breaks = c(0.0000, 0.002, 0.004, 0.006))

plot.igr.bwp
#note that n = 38 bugs with no bwp vs 11 with bwp

```

Export igr plot for no BWP/BWP
```{r}

#jpeg(filename="igr.bwp.jpeg", width=20, height=12, units="cm", pointsize=12, bg="white", res=600)
#plot.igr.bwp
#dev.off()

```


consumption rate by black wingpads
```{r}

options(scipen=10000)

plot.consumption.bwp <- ggplot()+
  theme_classic()+
  geom_bar(data=bwp.growth.consumption.3.4, aes(x=bwp.end, y=average_cons_bug_mg.mg.day, color=bwp.end, fill = bwp.end),
           width = 0.4, position = position_dodge(width=0.5), stat="identity")+  
  theme(axis.title.x = element_blank())+
   ylab(expression(atop(paste("Consumption Rate"), "(mg mg"^-1*" d"^-1*")")))+
  geom_errorbar(data=bwp.growth.consumption.3.4,
                aes(x=bwp.end, y= average_cons_bug_mg.mg.day,
                    ymin=average_cons_bug_mg.mg.day-se_cons_bug_mg.mg.day, 
                    ymax=average_cons_bug_mg.mg.day+se_cons_bug_mg.mg.day,
                    group=bwp.end),
                width=.2, position=position_dodge(width=0.5), color= "black")+
  theme(legend.position='none')+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  scale_x_discrete("bwp.end", labels = c("N" = "No black wingpads", "Y" = "Black wingpads"))+
  scale_color_manual(values=c("black","black"), guide="none")+
  scale_fill_manual(values=c("#EC9A29", "#143642"))+
  scale_y_continuous(limits = c(-0.03, 0.32), breaks = c(0.0, 0.1, 0.2, 0.3))

plot.consumption.bwp
#note that n = 38 bugs with no bwp vs 11 with bwp

```

Export plot of consumption -  no BWP/BWP
```{r}

#jpeg(filename="consumption.bwp.jpeg", width=20, height=12, units="cm", pointsize=12, bg="white", res=600)
#plot.consumption.bwp
#dev.off()

```


Plot of all growth data vs all consumption data -- *consumption rates averaged if there were multiple*. No effect for trial. Color by leaf species
Clean up the growth consumption dataframe
First, remove NA's from the df
Remove one huge consumption rate outlier -- consumption rate = 2.776
```{r}

growth_development_consumption_averaged.cleaned <- 
  growth_development_consumption_averaged %>% filter(!is.na(mean_bug_consumption))

growth_development_consumption_averaged.cleaned <- 
  growth_development_consumption_averaged.cleaned %>% filter(!mean_bug_consumption>2)

```


```{r}

growth.v.consumption.plot <- 
  ggplot(growth_development_consumption_averaged.cleaned,
         aes(x=mean_bug_consumption, y=igr, color=leaf))+
  theme_classic()+
  geom_point(data=growth_development_consumption_averaged.cleaned,
         aes(x=mean_bug_consumption, y=igr, color=leaf))+
   theme(legend.position = "right", legend.title = element_blank())+
   xlab(expression(atop(paste("Mass-specific consumption rate"), "(mg mg"^-1*" d"^-1*")")))+
   ylab(expression(atop(paste("Mass-specific growth rate"), "(mg mg"^-1*" d"^-1*")")))+
   scale_color_manual(values=c("#FEB72DFF", "#3F4788FF"),
                      labels=c(expression(paste(italic("Acer"))),expression(paste(italic("Rhododendron")))))+
  theme(legend.text=element_text(size=14))+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  theme(axis.text=element_text(size=14))+
  theme(axis.title=element_text(size=18))+
  theme(legend.text=element_text(size=14))+
  theme(legend.text.align=0)

growth.v.consumption.plot

```

Export the growth vs. consumption plot
```{r}

#jpeg(filename="growth_v_consumption.jpeg", width=20, height=12, units="cm", pointsize=12, bg="white", res=600)
#growth.v.consumption.plot
#dev.off()

```


Clean up the not-averaged gdc df
```{r}

growth_development_consumption.cleaned <- growth_development_consumption %>% 
  filter(!is.na(consumption.bug.mg.day.mcorr.modmasscorr))

growth_development_consumption.cleaned <- growth_development_consumption.cleaned %>%
  filter(!consumption.bug.mg.day.mcorr.modmasscorr>2)

#Trial-specific dataframes
growth_development_consumption.cleaned.CT1 <- growth_development_consumption.cleaned %>% filter(c.trial=="CT1")
growth_development_consumption.cleaned.CT2 <- growth_development_consumption.cleaned %>% filter(c.trial=="CT2")
growth_development_consumption.cleaned.CT3 <- growth_development_consumption.cleaned %>% filter(c.trial=="CT3")

```


linear mixed-effects models -- growth as a function of consumption, random effect for trial number and channel?
```{r}

model.growth.v.consumption <- lmer(igr~mean_bug_consumption*leaf + (1|channel),
                                   data=growth_development_consumption_averaged.cleaned)

summary(model.growth.v.consumption)
#no significant relationship between consumption and growth 


#Model with no leaf species interaction -- does igr depend on consumption overall (for data across both leaf species?)
model.growth.v.consumption.2 <- lmer(igr~mean_bug_consumption + (1|channel),
                                   data=growth_development_consumption_averaged.cleaned)

summary(model.growth.v.consumption.2)
#no significant relationship between consumption and growth

```






#####


Exploring patterns with fungal biomass

Read in data and add calculations back in (Vlad had done them in Excel, I will do them here in R)
Correcting for AFDM based on average ash fraction by leaf species calculated from all the microbe chambers in the whole experiment (see consumption rate file for these calcs) 
```{r}

fungal_biomass_SSC <- read.csv("Ergosterol_SSC_FB_2019_Cummins_cleaned_13Dec2023.csv")
fungal_biomass_SSC <- fungal_biomass_SSC %>% filter(!QC=="EXCL")

#ash fraction for Rhodo was 0.09529
#ash fraction for Acer was 0.18979

fungal_biomass_SSC <- fungal_biomass_SSC %>% mutate(dm_g = vial_litter_g - vial_mass_g)

fungal_biomass_SSC <- fungal_biomass_SSC %>% mutate(
  AFDM_g = case_when(
    species=="A" ~ (dm_g*(1-0.18979)),
    species=="R" ~ (dm_g*(1-0.09529)),
  )
)

fungal_biomass_SSC <- fungal_biomass_SSC %>% mutate(erg_ug_g_afdm = erg_sample_ug/AFDM_g)
fungal_biomass_SSC <- fungal_biomass_SSC %>% mutate(fb_mg_g_afdm = erg_ug_g_afdm/5.5)


fungal_biomass_SSC <- fungal_biomass_SSC %>% mutate(
  trial.name = case_when(
    trial=="CT1" ~ "Trial 1 - 12-20 March 2019",
    trial=="CT3" ~ "Trial 3 - 10-17 April 2019",
  )
)

fungal_biomass_summarized <- fungal_biomass_SSC %>%
  group_by(trial.name, treatment, species) %>%
  dplyr::summarise(mean_fb_mg_g_afdm=mean(fb_mg_g_afdm),
    sd_fb=sd(fb_mg_g_afdm),
    n_fb=n(),
    se_fb=sd_fb/sqrt(n_fb))

fungal_biomass_summarized <- fungal_biomass_summarized %>% 
  mutate(week=case_when(trial.name=="Trial 1 - 12-20 March 2019" ~ "Week 1 - 12-20 March 2019",
                        trial.name=="Trial 3 - 10-17 April 2019" ~ "Week 5 - 10-17 April 2019"))


```


Graph!
*MS Figure 5*
```{r}

plot.FB <- ggplot()+
  geom_bar(data=fungal_biomass_summarized, aes(x=treatment, y=mean_fb_mg_g_afdm, fill = species), width=1.5,
           position = position_dodge(width=1.5), stat="identity")+
  geom_errorbar(data=fungal_biomass_summarized, 
                aes(x=treatment, y= mean_fb_mg_g_afdm, ymin=mean_fb_mg_g_afdm-se_fb, ymax=mean_fb_mg_g_afdm+se_fb, group=species),
                width=.2, position=position_dodge(width=1.5), color= "black")+
  facet_wrap(~week)+
  scale_x_continuous(breaks=c(0,2,4),labels=c("+0째C", "+2째C", "+4째C"))+
  theme_classic()+
  theme(legend.position="right", legend.title = element_blank())+
  xlab("Temperature treatment")+
  ylab(expression(paste("Fungal biomass", " (mg gAFDM"^-1*")")))+
  scale_color_manual(values=c("black","black"), guide="none")+
  scale_fill_manual(values=c("#FEB72DFF", "#3F4788FF"),
                     labels=c(expression(paste(italic("Acer"))),
                              expression(paste(italic("Rhododendron")))))+
  theme(legend.text.align=0)+
  theme(legend.text=element_text(size=10))+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
    theme(strip.background = element_rect(color = "white"),
          strip.placement = "inside",
          strip.text = element_text(vjust = -1)) + 
    annotate("segment",x = -1,xend = 5,y = 54,yend = 54, size = 0.5,)+ 
       theme(strip.text.x = element_text(size = 12, face="bold"))+
  scale_y_continuous(breaks=c(0,10,20,30,40,50),labels=c("0","10","20","30","40","50"))

plot.FB


```


Export MS Figure 5
```{r}

#jpeg(filename="fb_by_trt.jpeg", width=20, height=12, units="cm", pointsize=12, bg="white", res=600)
#plot.FB
#dev.off()

```


Plot of channel-level consumption vs. fungal biomass
First, get channel-level average consumption for each trial
```{r}

#remove NA's and outlier from consumption data
consumption <- consumption %>% filter(!is.na(consumption.bug.mg.day.mcorr.modmasscorr))
consumption <- consumption %>% filter(!consumption.bug.mg.day.mcorr.modmasscorr>2)

consumption_1_3 <- consumption %>% filter(c.trial=="CT1" | c.trial=="CT3")
consumption_1_3_024 <- consumption_1_3 %>% filter(treatment=="0" | treatment=="2" | treatment=="4")

consumption_1_3_024_channelave <- consumption_1_3_024 %>% group_by(c.trial, c.trial.mean.temp.C, treatment, leaf, channel) %>% 
  dplyr::summarise(mean_consumption_bug=mean(consumption.bug.mg.day.mcorr.modmasscorr),
            sd_bug_c=sd(consumption.bug.mg.day.mcorr.modmasscorr),
            n_bug_c=n(),
            se_bug=sd_bug_c/sqrt(n_bug_c))

consumption_1_3_024_channelave <- consumption_1_3_024_channelave %>% 
           dplyr::rename("species" = "leaf",
                  "trial" = "c.trial")

```


join consumption data to fb data
```{r}

fungal_biomass_SSC <- fungal_biomass_SSC %>% mutate(species=case_when(species=="A" ~ "Acer",
                                                     species=="R" ~ "Rhodo"))

fb_consumption <- left_join(fungal_biomass_SSC, consumption_1_3_024_channelave)
fb_consumption_R <- fb_consumption %>% filter(species=="Rhodo") 
fb_consumption_A <- fb_consumption %>% filter(species=="Acer") 

```


Models - consumption vs. fb
```{r}

model_consumption_fb <- lmer(mean_consumption_bug ~ fb_mg_g_afdm + (1|trial), data=fb_consumption)
summary(model_consumption_fb)

model_consumption_fb_A <- lmer(mean_consumption_bug ~ fb_mg_g_afdm + (1|trial), data=fb_consumption_A)
summary(model_consumption_fb_A)
#no relationship

model_consumption_fb_R <- lmer(mean_consumption_bug ~ fb_mg_g_afdm + (1|trial), data=fb_consumption_R)
summary(model_consumption_fb_R)
#higher FB = lower consumption for Rhodo but there is a very small range in FB
#but higher temp = higher consumption for Rhodo.....
pred.model_consumption_fb_R <- ggpredict(model_consumption_fb_R, terms="fb_mg_g_afdm")

fb_consumption$species <- as.factor(fb_consumption$species)

model_consumption_fb <- lmer(mean_consumption_bug ~ fb_mg_g_afdm*species + (1|trial), data=fb_consumption)
summary(model_consumption_fb)

#fb_consumption$species <- factor(fb_consumption$species, levels=rev(levels(fb_consumption$species)))

```

```{r}

fb_consumption_plot <- 
  ggplot(fb_consumption, aes(x=fb_mg_g_afdm, y=mean_consumption_bug, color=species, shape=trial))+
  theme_classic()+
  geom_point(data=fb_consumption, aes(x=fb_mg_g_afdm, y=mean_consumption_bug, color=species, shape=trial))+
   theme(legend.position = "right", legend.title = element_blank())+
   xlab(expression(paste("Fungal biomass", " (mg gAFDM"^-1*")")))+
   ylab(expression(atop(paste("Mass-specific consumption rate"), "(mg mg"^-1*" d"^-1*")")))+
   scale_color_manual(values=c("#FEB72DFF", "#3F4788FF"),
                      labels=c(expression(paste(italic("Acer"))),expression(paste(italic("Rhododendron")))))+
  theme(legend.text=element_text(size=14))+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  theme(axis.text=element_text(size=14))+
  theme(axis.title=element_text(size=18))+
  theme(legend.text=element_text(size=14))+
  theme(legend.text.align=0)

fb_consumption_plot

```

Acer
```{r}

fb_consumption_plot_A <- 
  ggplot(fb_consumption_A, aes(x=fb_mg_g_afdm, y=mean_consumption_bug, shape=trial))+
  theme_classic()+
  geom_point(data=fb_consumption_A, aes(x=fb_mg_g_afdm, y=mean_consumption_bug, shape=trial), color="#FEB72DFF", size=2)+
   theme(legend.position = "right", legend.title = element_blank())+
   xlab(expression(paste("Fungal biomass", " (mg gAFDM"^-1*")")))+
   ylab(expression(atop(paste("Mass-specific consumption rate"), "(mg mg"^-1*" d"^-1*")")))+
  theme(legend.text=element_text(size=14))+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  theme(axis.text=element_text(size=14))+
  theme(axis.title=element_text(size=18))+
  theme(legend.text=element_text(size=14))+
  theme(legend.text.align=0)+
  theme(axis.title.y=element_blank())

fb_consumption_plot_A

```

Rhodo
```{r}

fb_consumption_plot_R <- 
  ggplot(fb_consumption_R)+
  theme_classic()+
  geom_line(data=pred.model_consumption_fb_R, aes(x=x, y=predicted), color="#3F4788FF")+
  geom_ribbon(data=pred.model_consumption_fb_R, aes(x = x, ymin = conf.low, ymax = conf.high, ),
              alpha = 0.25, fill="#3F4788FF", show.legend=F)+
  geom_point(data=fb_consumption_R, aes(x=fb_mg_g_afdm, y=mean_consumption_bug, shape=trial), color="#3F4788FF", size=2)+
   theme(legend.position = "right", legend.title = element_blank())+
   xlab(expression(paste("Fungal biomass", " (mg gAFDM"^-1*")")))+
   ylab(expression(atop(paste("Mass-specific consumption rate"), "(mg mg"^-1*" d"^-1*")")))+
  theme(legend.text=element_text(size=14))+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  theme(axis.text=element_text(size=14))+
  theme(axis.title=element_text(size=18))+
  theme(legend.text=element_text(size=14))+
  theme(legend.text.align=0)
fb_consumption_plot_R

```


```{r}

#jpeg(filename="consumption_v_fb.jpeg", width=20, height=12, units="cm", pointsize=12, bg="white", res=600)
#fb_consumption_plot
#dev.off()

```

Fungal biomass analysis

Plot - scatter for temp vs. fb
```{r}

fb_temp_plot <- 
  ggplot(fb_consumption, aes(x=c.trial.mean.temp.C, y=fb_mg_g_afdm, color=species, shape=trial))+
  theme_classic()+
  geom_point(data=fb_consumption, aes(x=c.trial.mean.temp.C, y=fb_mg_g_afdm, color=species, shape=trial))+
   theme(legend.position = "right", legend.title = element_blank())+
   xlab("Mean Temperature (째C)")+
   ylab(expression(paste("Fungal biomass (mg g"^-1*" AFDM")))+
   scale_color_manual(values=c("#FEB72DFF", "#3F4788FF"),
                      labels=c(expression(paste(italic("Acer"))),expression(paste(italic("Rhododendron")))))+
  theme(legend.text=element_text(size=14))+
  theme(axis.title=element_text(size=14))+
  theme(axis.text=element_text(size=12, face="bold"))+
  theme(axis.text=element_text(size=14))+
  theme(axis.title=element_text(size=18))+
  theme(legend.text=element_text(size=14))+
  theme(legend.text.align=0)

fb_temp_plot

```


```{r}

fb_consumption$species <- as.factor(fb_consumption$species)
fb_consumption_A$species <- as.factor(fb_consumption_A$species)
fb_consumption_R$species <- as.factor(fb_consumption_R$species)

model_fb_temp.lmer <- lmer(fb_mg_g_afdm ~ c.trial.mean.temp.C*species + (1|trial), data=fb_consumption)
summary(model_fb_temp.lmer)

#fb_consumption$species <- factor(fb_consumption$species, levels=rev(levels(fb_consumption$species)))#run to reverse factor levels

#lmer model for temperature with trial as a fixed effect

model_fb_temp.trial.lm <- lm(fb_mg_g_afdm ~ c.trial.mean.temp.C*species + trial*species, data=fb_consumption)
summary(model_fb_temp.trial.lm)

```

ANOVA's to compare FB by temp treatment and trial 
```{r}
fb_consumption$treatment <- as.factor(fb_consumption$treatment)
fb_consumption$trial_treatment <- paste(fb_consumption$trial, fb_consumption$treatment, sep="_")

anova_fb_treatment_trial <- aov(fb_mg_g_afdm~trial_treatment*species, data=fb_consumption)
summary(anova_fb_treatment_trial)

anova_fb_trial <- aov(fb_mg_g_afdm~trial*species, data=fb_consumption)
summary(anova_fb_trial)

anova_fb_treatment <- aov(fb_mg_g_afdm~treatment*species, data=fb_consumption)
summary(anova_fb_treatment)

TukeyHSD(anova_fb_treatment_trial)
#extremely complicated pairwise comparisons table

TukeyHSD(anova_fb_trial)
TukeyHSD(anova_fb_treatment)

```

Creating and exporting MS Figure S3 
```{r}

library(cowplot)
consumption_FB_byleaf <- plot_grid(fb_consumption_plot_R, fb_consumption_plot_A, labels = c('A', 'B'))
consumption_FB_byleaf

```

```{r}

#jpeg(filename="consumption_FB_byleaf.jpeg", width=45, height=20, units="cm", pointsize=12, bg="white", res=600)
#consumption_FB_byleaf
#dev.off()

```

